Manuscript_Github_Pchabaudi_qusage

### 2022-08-05 chapter4_results_chabaudi24h/Thesis_Github_Pchabaudi_qusage.Rmd
qusage rmd title and intro

---
title: "Manuscript_Github_Pchabaudi_boilerplate"
author: "Timothy Little"
date: "29/07/2022"
output: html_document
---

Looking at GO enrichment of genes in- and out-of-phase between the 24 asexual life cycles of rMT and SBP transmitted P. chabaudi.

@@

ht <- Heatmap(transStages_ht.mat.t,
        cluster_rows = FALSE,
        cluster_columns = FALSE,
        cluster_column_slices = FALSE,
        na_col = 'white',
        #Use factors to keep the ordering that we want.
        row_split = factor(str_extract(colnames(transStages_ht.mat),
                                   pattern = 'pirs|^L|^S|AAPL|ChAPL'),
                              levels = unique(str_extract(colnames(transStages_ht.mat),
                                   pattern = 'pirs|^L|^S|AAPL|ChAPL'))),
        row_order = colnames(transStages_ht.mat),
        row_gap = unit(.5,"cm"),
        row_names_gp = gpar(fontsize = 9),
        column_split = factor(str_extract(rownames(transStages_ht.mat),
                                   pattern = 'rMT|SBP'),
                              levels = unique(str_extract(rownames(transStages_ht.mat),
                                   pattern = 'rMT|SBP'))),
        column_gap = unit(.3, "cm"),
        border = TRUE,
        #Using this colour scheme because mincol is a lot less negative 
        # than maxcol is positive
        col = colorRamp2(c(mincol,
                           0,
                           maxcol/4,
                           maxcol/2,
                           maxcol),
                         c('blue', 'white', 'yellow', 'orange', 'red')),
        heatmap_legend_param = list(title = 'LogFoldChange'))
draw(ht)
```

>>>>

---
title: "Manuscript_Github_Pchabaudi_qusage"
author: "Timothy Little"
date: "29/07/2022"
output: html_document
---

Qusage analysis of gene set enrichment (e.g. pirs, L-forms, ChAPL loci) between the transmission methods and timepoints of the asexual life cycle.

@@

ht <- Heatmap(transStages_ht.mat.t,
        cluster_rows = FALSE,
        cluster_columns = FALSE,
        cluster_column_slices = FALSE,
        na_col = 'white',
        #Use factors to keep the ordering that we want.
        row_split = factor(str_extract(colnames(transStages_ht.mat),
                                   pattern = 'pirs|^L|^S|AAPL|ChAPL'),
                              levels = unique(str_extract(colnames(transStages_ht.mat),
                                   pattern = 'pirs|^L|^S|AAPL|ChAPL'))),
        row_order = colnames(transStages_ht.mat),
        row_gap = unit(.5,"cm"),
        row_names_gp = gpar(fontsize = 9),
        column_split = factor(str_extract(rownames(transStages_ht.mat),
                                   pattern = 'rMT|SBP'),
                              levels = unique(str_extract(rownames(transStages_ht.mat),
                                   pattern = 'rMT|SBP'))),
        column_gap = unit(.3, "cm"),
        border = TRUE,
        #Using this colour scheme because mincol is a lot less negative 
        # than maxcol is positive
        col = colorRamp2(c(mincol,
                           0,
                           maxcol/4,
                           maxcol/2,
                           maxcol),
                         c('blue', 'white', 'yellow', 'orange', 'red')),
        heatmap_legend_param = list(title = 'LogFoldChange'))
if(global_save_var){
  pdf(file = 'plots/stagesWithinTrans_logFoldheatmap.pdf',
      height = 8,
      width = 6)
  draw(ht)
  dev.off()
}
```
